An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2022-03-27 simplified_sdc_intro/paper.tex
more net details

Our final set of nuclei are $\mathrm{n}$, ${}^{1}\mathrm{H}$,
${}^{4}\mathrm{He}$, ${}^{12}\mathrm{C}$, ${}^{14}\mathrm{C}$,
${}^{13}\mathrm{N}$, ${}^{14}\mathrm{N}$, ${}^{16}\mathrm{O}$,
${}^{18}\mathrm{O}$, ${}^{18}\mathrm{F}$, ${}^{20}\mathrm{Ne}$,
${}^{21}\mathrm{Ne}$, ${}^{22}\mathrm{Ne}$, ${}^{22}\mathrm{Na}$,
${}^{23}\mathrm{Na}$, ${}^{23}\mathrm{Mg}$, ${}^{24}\mathrm{Mg}$,
${}^{27}\mathrm{Al}$, ${}^{27}\mathrm{Si}$, ${}^{28}\mathrm{Si}$,
${}^{31}\mathrm{P}$, ${}^{31}\mathrm{S}$, ${}^{32}\mathrm{S}$,
${}^{35}\mathrm{Cl}$, ${}^{36}\mathrm{Ar}$, ${}^{39}\mathrm{K}$,
${}^{40}\mathrm{Ca}$, ${}^{43}\mathrm{Sc}$, ${}^{44}\mathrm{Ti}$,
${}^{47}\mathrm{V}$, ${}^{48}\mathrm{Cr}$, ${}^{51}\mathrm{Mn}$,
${}^{52}\mathrm{Fe}$, ${}^{55}\mathrm{Co}$, ${}^{56}\mathrm{Ni}$.  The 119
rates linking them are given in table ~\ref{table:rates}, with the
forward rates having a positive $Q$ value and the reverse having a
negative $Q$ value.  We add screening to the rates using the prescription
from The C++ code for the network is output by \pynucastro\
directly for \castro.  A graphical overview of the network showing the links
between the nuclei is shown in figure~\ref{fig:subch_network}.

>>>>

Our final set of 35 nuclei are $\mathrm{n}$, ${}^{1}\mathrm{H}$,
${}^{4}\mathrm{He}$, ${}^{12}\mathrm{C}$, ${}^{14}\mathrm{C}$,
${}^{13}\mathrm{N}$, ${}^{14}\mathrm{N}$, ${}^{16}\mathrm{O}$,
${}^{18}\mathrm{O}$, ${}^{18}\mathrm{F}$, ${}^{20}\mathrm{Ne}$,
${}^{21}\mathrm{Ne}$, ${}^{22}\mathrm{Ne}$, ${}^{22}\mathrm{Na}$,
${}^{23}\mathrm{Na}$, ${}^{23}\mathrm{Mg}$, ${}^{24}\mathrm{Mg}$,
${}^{27}\mathrm{Al}$, ${}^{27}\mathrm{Si}$, ${}^{28}\mathrm{Si}$,
${}^{31}\mathrm{P}$, ${}^{31}\mathrm{S}$, ${}^{32}\mathrm{S}$,
${}^{35}\mathrm{Cl}$, ${}^{36}\mathrm{Ar}$, ${}^{39}\mathrm{K}$,
${}^{40}\mathrm{Ca}$, ${}^{43}\mathrm{Sc}$, ${}^{44}\mathrm{Ti}$,
${}^{47}\mathrm{V}$, ${}^{48}\mathrm{Cr}$, ${}^{51}\mathrm{Mn}$,
${}^{52}\mathrm{Fe}$, ${}^{55}\mathrm{Co}$, ${}^{56}\mathrm{Ni}$.  The 119
rates linking them are given in table~\ref{table:rates}, with the
forward rates having a positive $Q$ value and the reverse having a
negative $Q$ value.  We add screening to the rates using the prescription
from \citet{graboske:1973,alastuey:1978,itoh:1979}.  The C++ code for the network is output by \pynucastro\
directly for \castro.  A graphical overview of the network showing the links
between the nuclei is shown in figure~\ref{fig:subch_network}.
